A large-scale analysis of racial disparities in police stops across the United

### 2019-12-10 lib/paper_results.Rmd
fixing paper results

```{r search_rates}
tbl <- pfs$rates$search %>% 
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    average_search_rate = mean(search_rate),
    average_n = mean(n),
    std_error = sqrt(
      average_search_rate * (1 - average_search_rate) / average_n
    ),
    CI_radius = 1.96 * std_error,
    CI_lower = average_search_rate - CI_radius,
    CI_upper = average_search_rate + CI_radius
  ) %>%
  ungroup()
tbl %>% kable()
```

@@

```{r}

```

@@

Number of stops in 7:00-7:15pm panel:
`r vod$full$plots$states$TX$`7:00pm`$data$n %>% sum() %>% comma_num()`

Number of stops in 7:15-7:30pm panel:
`r vod$full$plots$states$TX$`7:15pm`$data$n %>% sum() %>% comma_num()`

Number of stops in 7:30-7:45pm panel:
`r vod$full$plots$states$TX$`7:30pm`$data$n %>% sum() %>% comma_num()`

Total number of stops in 3 panels:
`r comma_num(vod$full$plots$states$TX$`7:00pm`$data$n %>% sum() + vod$full$plots$states$TX$`7:15pm`$data$n %>% sum() +  vod$full$plots$states$TX$`7:30pm`$data$n %>% sum())`

@@

City and State outcomes:
```{r disparity-hit_rates-tables}
rbind(
  disp$city$outcome$results$aggregate_hit_rates %>% 
    mutate(
      geography = "cities",
      std_error = sqrt(hit_rate * (1 - hit_rate) / n),
      lower_CI = hit_rate - 1.96 * std_error,
      upper_CI = hit_rate + 1.96 * std_error
    ),
  disp$state$outcome$results$aggregate_hit_rates %>% 
    mutate(
      geography = "states",
      std_error = sqrt(hit_rate * (1 - hit_rate) / n),
      lower_CI = hit_rate - 1.96 * std_error,
      upper_CI = hit_rate + 1.96 * std_error
    )
) %>% 
  select(-std_error) %>% 
  select(geography, everything())
  kable()
```

>>>>

```{r search_rates}
tbl <- pfs$rates$search %>% 
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    average_n = mean(n),
    average_n_searches = mean(n_searches),
    average_search_rate = mean(search_rate),
    std_error = sqrt(
      average_search_rate * (1 - average_search_rate) / average_n
    ),
    CI_radius = 1.96 * std_error,
    CI_lower = average_search_rate - CI_radius,
    CI_upper = average_search_rate + CI_radius
  ) %>%
  ungroup()
tbl %>% kable()
prop_tbl <- tbl %>%
  mutate(
    n_success = average_n_searches,
    n_failure = average_n - average_n_searches
  )
```

p-values:

@@

@@

Number of stops in 7:00-7:15pm panel:
```{r}
vod$full$plots$states$TX$`7:00pm`$data$n %>% sum() %>% comma_num()
```

Number of stops in 7:15-7:30pm panel:
```{r}
vod$full$plots$states$TX$`7:15pm`$data$n %>% sum() %>% comma_num()
```

Number of stops in 7:30-7:45pm panel:
```{r}
vod$full$plots$states$TX$`7:30pm`$data$n %>% sum() %>% comma_num()
```

Total number of stops in 3 panels:
```{r}
comma_num(vod$full$plots$states$TX$`7:00pm`$data$n %>% sum() + vod$full$plots$states$TX$`7:15pm`$data$n %>% sum() +  vod$full$plots$states$TX$`7:30pm`$data$n %>% sum())
```

@@

City and State outcomes:
```{r disparity-hit_rates-tables}
rbind(
  disp$city$outcome$results$aggregate_hit_rates %>% 
    mutate(
      geography = "cities",
      std_error = sqrt(hit_rate * (1 - hit_rate) / n),
      lower_CI = hit_rate - 1.96 * std_error,
      upper_CI = hit_rate + 1.96 * std_error
    ),
  disp$state$outcome$results$aggregate_hit_rates %>% 
    mutate(
      geography = "states",
      std_error = sqrt(hit_rate * (1 - hit_rate) / n),
      lower_CI = hit_rate - 1.96 * std_error,
      upper_CI = hit_rate + 1.96 * std_error
    )
) %>% 
  select(-std_error) %>% 
  select(geography, everything()) %>%
  kable()
```
